
\begin{enumerate}
\item 
\question{If I have an RC circuit with a resistor of $10\myohm$ and a capacitor of $2\myf$, what is the RC time constant of this circuit?}
\solution{$20$ seconds}
\explanation{The RC time constant is just the resistance (in ohms) multiplied by the capacitance (in farads).
Therefore, multiply $10\cdot 2 = 20$.
The time constant is $20$ seconds.
}
\item 
\question{In the previous question, how many seconds does it take to charge my capacitor to approximately 50\% of supply voltage?}
\solution{$14$ seconds}
\explanation{Figure~\ref{figTimeConstants} shows how many time constants it takes to charge a capacitor to a certain percentage of supply voltage.
Like most things in electronics, it won't be exact.
However, in the figure you can see that $0.7$ time constants will yield 50.3\% of the supply voltage.
Since the time constant was $20$ seconds, the amount of time to charge 50\% is $0.7\cdot 20 = 14$ seconds.
}
\item 
\question{If I have an RC circuit with a resistor of $30,000\myohm$ and a capacitor of $0.001\myf$, what is the RC time constant of this circuit?}
\solution{$30$ seconds}
\explanation{The RC time constant is just resistance (in ohms) multiplied by capacitance (in farads).
In this case, that yields $30,000 \cdot 0.001 = 30$ seconds.
}
\item 
\question{In the previous question, what percentage of the way is the capacitor's voltage charged after 60 seconds?}
\solution{86.5\%}
\explanation{Since the RC time constant is 30 seconds, 60 seconds would be two RC time constants.
Figure~\ref{figTimeConstants} shows that two time constants yields an 86.5\% voltage charge.}
\item 
\question{If I have an RC circuit with a resistor of $25\mykohm$ and a capacitor of $20\myuf$, what is the RC time constant of this circuit?}
\solution{$0.25$ seconds}
\explanation{This is just like the other time constant problems, except that we have to change units.
The units for the RC circuit are ohms and farads.
Since $1\mykohm = 1,000\myohm$, then $25\mykohm = 25,000\myohm$.
Likewise, since $1\myuf = 0.000001\myf$, then $20\myuf = 0.00002\myf$.

Now we just need to multiply them together.
$25,000 \cdot 0.00002 = 0.5$ seconds.
}
\item 
\question{Give a resistor and capacitor combination that will yield an RC time constant of 0.25 seconds.}
\solution{Any resistor/capacitor combination that, when multiplied together, yields $0.25$ will suffice.  A simple example would be to halve \emph{one} of the component values from the previous problem. For instance, I could keep the $25\mykohm$ resistor but change the capacitor to $10\myuf$.}
\item 
\question{Reconfigure the circuit in Figure~\ref{figSimpleTimerCircuit} to wait for 3 seconds.  Draw the whole circuit.}
% FIXME - need solution
\item 
\question{Redraw the previous circuit, and circle each basic circuit pattern and label it.}
% FIXME - need solution
\end{enumerate}
