
\begin{enumerate}
\item As the frequency of a signal goes up, how does that affect the reactance from a capacitor?  What about with an inductor?
\item As the frequency of a signal goes down, how does that affect the reactance from a capacitor?  What about with an inductor?
\item What is true about the relationship between the capacitative reactance and the inductive reactance at the resonant frequency?
\item Why is power not used up with reactance?
\item How are reactance and resistance combined to yield impedance?
\item Calculate the capacitative reactance of a $3\myf$ capacitor at $5\myhz$.
\item Calculate the capacitative reactance of a $20\myuf$ capacitor at $200\myhz$.
\item Calculate the inductive reactance of a $7\myhy$ inductor at $10\myhz$.
\item Calculate the inductive reactance of a $8\mymhy$ inductor at $152\myhz$.
\item Calculate the impedance of a circuit with a $200\myohm$ resistor in series with a $75\myuf$ capacitor with a signal of $345\myhz$.
\item Calculate the impedance of a circuit with a $310\myohm$ resistor in series with a $90\mynf$ capacitor with a signal of $800\myhz$.
\item Calculate the impedance of a circuit with no resistor and a $60\mymhy$ inductor with a signal of $89\myhz$.
\item Calculate the impedance of a circuit with a $50\myohm$ resistor in series with a $75\myuhy$ inductor with a signal of $255\myhz$.
\item If I have an AC circuit with an RMS voltage of $6\myvolt$ and an impedance of $1\mykohm$, what is the average (RMS) current of this circuit?
\item If I have an AC circuit, and I measure the AC voltage as $10\myvolt$ RMS, and I measure the AC current at $2\mymamp$ RMS, what is the impedance of this circuit?
\item If I have an $80\myhz$ AC circuit that has an $8\myvolt$ RMS voltage source in series with a $500\myohm$ resistor, a $5\myhy$ inductor, and a $200\mynf$ capacitor, what is the RMS current flowing in this circuit?
\item Calculate the impedance of a circuit with a $250\myohm$ resistor in series with a $87\myuhy$ inductor and a $104\myuf$ capacitor with a signal of $745\myhz$.
\item What is the resonant frequency of the circuit in the previous question?
\item What is the reactance of a circuit at its resonant frequency?
\item If I have a $10\myuf$ capacitor, what size inductor do I need to have a resonant frequency of $250\myhz$?
\end{enumerate}
