
\begin{enumerate}
\item If I want a circuit to block DC current but allow AC current, should I use an inductor or a capacitor?
\item If I want a circuit to allow DC current but block AC current, should I use an inductor or a capacitor?
\item Why are inductors used so much in systems that interact with the outside world?
\item Why does inductive kick happen?
\item Draw a schematic of an inductor where the positive side of the inductor has a switch and the negative side is connected to an LED and a resistor.  Add in a snubber diode to protect the LED from the effect of turning off the switch.
\item If I have an inductor that is $5\myhy$ and has a steady current going through it of $2\myamp$, what is the size of the magnetic flux in the inductor's magnetic field?
\item If I have an inductor that is $7\myuhy$ and has a steady current going through it of $3\mymamp$, what is the size of the magnetic flux in the inductor's magnetic field?
\item If I have a $4\myhy$ inductor with $0.3\mywb$ of flux in its magnetic field, how much current is flowing through it?
\item If an inductor's magnetic field has $5\mywb$ of flux and it decreases to $3\mywb$ of flux over $2\mysec$, what is the average voltage produced over that timeframe?
\item If an inductor's magnetic field has $1\myuwb$ of flux and it increates to $2\myuwb$ of flux over $0.4\mysec$, what is the average voltage produced over that timeframe?
\item If the current flowing through a $3\myhy$ inductor drops from $7\mymamp$ to $1\mymamp$ over a period of $0.01\mysec$, what is the average voltage produced over that time period?
\end{enumerate}
