
\begin{enumerate}
\item 
\question{Practice modifying and uploading the Blink program to the Arduino Uno.  Change the numbers given to \icode{delay} to different values, and see how that affects the operation of the program.}
\solution{Changing the value for the delay should cause the light to noticeably blink at different rates.}
\item 
\question{The ATmega328/P is only one of many different microcontrollers available in the AVR family.  Research online to find one or two other AVR chips and what different features they have.}
\solution{There are many different types of AVR chips.  Some of the others include the ATTiny series, the ATmega series, and the XMEGA.  These chips generally differ by available memory, number of pins, and add-on subsystems.}
\item 
\question{The AVR family is only one of many microcontroller families.  Research one or two other microcontroller families and look at what features are claimed for each.  Examples of other microcontroller families include: PIC, STM32, MSP432, and the Intel Quark.}
\solution{This is an open-ended question.  Features that would be interesting to focus on are power consumption, working voltage, available memory, ease of programming, extra features, size, and other characteristics.}
\item 
\question{Go to the \icode{arduino.cc} website and look at the different types of Arduinos that are available.  What makes them different?  Why might you choose one for a project over another?}
\solution{While Arduino continually comes out with new variants, some popular variants include the Arduino Uno, the Leonardo, the 101, the Nano, the MKR series, the M0, the Due, and others.  These differ from each other based on size, the microcontroller family (AVR, Intel, etc.), the specific microcontroller (which varies based on RAM, speed, power consumption, extra features, etc.), and the extras packed onto the board.  The MKR series, for instance, combines the microcontroller with different kinds of networking features.  Also, some of them vary by the working voltages used as well.  Some variants such as the Lilypad are geared towards wearable devices.}
\end{enumerate}
